### 2016-07-11 lineups.Rnw
not feeling good today but still committed to the streak!
small amount more about estimation

@@

\hh{The pilot study consisted of an evaluation of a set of 20 lineups by 11 volunteers. For each of the model situations ($M_1$ vs $M_2$, $M_2$ vs $M_1$, $M_1$ vs $M_3$ and $M_3$ vs $M_1$) one lineup of size $m = 3, 6, 9, 12$ was used. Overall, the number of data identifications in the lineups was very low (34 out of 220 evaluations). Participants identified the data plot in two to four of the lineups they evaluated. The mode was three data identifications. }
\paragraph{Suitability of $M_3$ in lineups:}
\begin{figure}
\centering
<<data-picks, echo=FALSE, fig.width=10, fig.height=5, out.width='0.85\\linewidth'>>=
pdffiles <- dir("GGExperimentApr28/", pattern="pdf")
pdffiles <- gsub(".pdf","",pdffiles)
#pdffiles <- gsub("-m","",pdffiles)
#pdffiles <- gsub("-rep","",pdffiles)

>>>>

\st{Because the likelihood function for these complicated models is intractable, RSiena implements a Monte Carlo simulation to obtain method of moments estimates of the parameter values. This fitting procedure was first introduced in ~\cite{saompaper}. }

@@

\hh{The pilot study consisted of an evaluation of a set of 20 lineups by 11 volunteers. For each of the model situations ($M_1$ vs $M_2$, $M_2$ vs $M_1$, $M_1$ vs $M_3$ and $M_3$ vs $M_1$) one lineup of size $m = 3, 6, 9, 12$ was used. Overall, the number of data identifications in the lineups was very low (34 out of 220 evaluations). Participants identified the data plot in two to four of the lineups they evaluated. The mode was three data identifications out of twenty per participant. }
\paragraph{Suitability of $M_3$ in lineups:}
\begin{figure}
\centering
<<data-picks, echo=FALSE, fig.width=10, fig.height=5, out.width='0.85\\linewidth'>>=
pdffiles <- dir("GGExperimentApr28/", pattern="pdf")
pdffiles <- gsub(".pdf","",pdffiles)
#pdffiles <- gsub("-m","",pdffiles)
#pdffiles <- gsub("-rep","",pdffiles)
